Development of Physics or HPC Optimisation of a parallel 2D lattice Boltzmann solver using GPUs/CUDA

### 2017-08-13 Thesis/Draft.tex
working on 3d

\subsection{3D model}
Similarly to the previous Section, we will now present the results obtained using the 3D model. Each result was obtained using a Cube-like mesh containing 128 nodes in all directions. Although this was not the mesh used when developing the solver, it is the one where we can best see the effects of our parallelization. However, using this mesh takes long amounts of time to compute under 10000 iterations. For this reason, the following tests were obtained using only Delta and Grid. 
\subsubsection{Enhanced distribution function v1.0}
\subsubsection{Final version v1.1}
\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{Hardware}
\subsection{Double vs Single}
\chapter{Conclusions}

>>>>

\subsection{3D model}
Similarly to the previous Section, we will now present the results obtained using the 3D model. Each result was obtained using a Cube-like mesh containing 128 nodes in all directions. Although this was not the mesh used when developing the solver, it is the one where we can best see the effects of our parallelization. However, using this mesh takes long amounts of time to compute under 10000 iterations. For this reason, the following tests were obtained using only Delta and Grid. 
\subsubsection{Enhanced distribution function v1.0}
Unlike in the 2D model, in the 3D version we decided to start the implementation using the enhanced distribution function. This was mainly influenced by the fact that most relevant papers regarding this topic also used this enhanced distribution function. Since they presented the best way to validate our results, we decided to also use this version directly.

  \begin{figure}[H]
  	\centering
  	\includegraphics[width=\linewidth]{Resources/Images/v13d.png}
  	\caption{Runtime comparison for version 1.0 on the Grid}
  	\label{fig:v13d}
  \end{figure}

 However, this version suffered from portability issues in Delta, most likely due to faulty memory accesses. Figure \ref{fig:v13d} shows the run-times for version 1.0 in the Grid. We now have much bigger run-times since the scale of the program has also increased. Now, the difference between double and single precision is much more noticeable, and so will, hopefully, the changes between optimizations.

\subsubsection{Final version v1.1}
\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{Hardware}
\subsection{Double vs Single}
\chapter{Conclusions}
